Forecasting the 2024 US General Election

### 2024-11-04 paper/paper.qmd
refine model section
Update paper.qmd
minor change in titel and abstract

---
title: "Forecasting the 2024 US General Election"
subtitle: "Analyzing the Impact of Swing States on Election Outcomes Using 538's 2024 General Election Dataset"
author: 
  - Tara Chakkithara
  - Sakura Hu
  - Luka Tosic
thanks: "Code and data are available at https://github.com/LukaTosic09/Forecasting-2024-Election"
date: today
date-format: long
abstract: "This paper forecasts the outcome of the 2024 U.S. general election. Using the poll of polls approach, a bayesian hierarchical model was developed with data from FiveThirtyEight using polling data from July 21 to October 19, 2024. The model's prediction is based on the electoral college vote in the seven key swing states : Arizona, Nevada, Michigan, Georgia, Wisconsin, Pennsylvania, and North Carolina to estimate the overall winner. Results indicate that Harris is predicted to win with a probaility of 66%."
format: pdf
number-sections: true
toc: true
bibliography: references.bib
---

@@

This paper focuses on forecasting the election outcome by employing the "poll of polls" method, utilizing data from FiveThirtyEight, along with historical data from the 2016 Clinton vs. Trump election and the 2020 Trump vs. Biden election. A Bayesian updating and Monte Carlo Simulations is created to predict the winner of the election outcome based on the popular vote across these swing states[some more details for what was done?]. The primary estimand in this analysis is the probability distribution of Harris's win percentage, derived from current polling data and historical election results. The model predicted that Harris will win, and [add details to result]

@@

## Posterior Predictive Check

>>>>

---
title: "Forecasting the 2024 US General Election"
subtitle: "Analyzing Swing State Impact on 2024 Election Outcomes: Bayesian Hierarchical Model Using 538's Data Predicts 66% Harris Victory"
author: 
  - Tara Chakkithara
  - Sakura Hu
  - Luka Tosic
thanks: "Code and data are available at https://github.com/LukaTosic09/Forecasting-2024-Election"
date: today
date-format: long
abstract: "This paper forecasts the outcome of the 2024 U.S. general election. Using the poll of polls approach, a Bayesian hierarchical model was developed with data from FiveThirtyEight using polling data from July 21 to October 19, 2024. The model's prediction is based on the electoral college vote in the seven key swing states: Arizona, Nevada, Michigan, Georgia, Wisconsin, Pennsylvania, and North Carolina to estimate the overall winner. Results indicate that Harris is predicted to win with a probability of 66%."
format: pdf
number-sections: true
toc: true
bibliography: references.bib
---

@@

This paper focuses on forecasting the election outcome by employing the "poll of polls" method, utilizing data from FiveThirtyEight, along with historical data from the 2016 Clinton vs. Trump election and the 2020 Trump vs. Biden election. A Bayesian updating and Monte Carlo Simulations are created to predict the winner of the election outcome based on the popular vote across these swing states[some more details for what was done?]. The estimand in this analysis is the probability distribution of Harris's win percentage, derived from current polling data and historical election results. The model predicted that Harris would win, and [add details to result]

@@
